Trans-Dimensional Inference for Gravitational Lens Substructures

### 2015-06-14 Papers/ms.tex
General philosophy for our priors

\section{Prior Probability Distributions}
The prior probability distributions for all hyperparameters, parameters, and
the data, are given in Table~\ref{tab:priors}, and a factorization of the
joint distribution is displayed in Figure~\ref{fig:pgm}.

>>>>

\section{Prior Probability Distributions}
The prior probability distributions for all hyperparameters, parameters, and
the data, are given in Table~\ref{tab:priors}, and a factorization of the
joint distribution is displayed in Figure~\ref{fig:pgm}. With these priors,
we aim to express a large degree of prior uncertainty (hence the liberal use
of uniform, loguniform, and Cauchy distributions). However, we also specify
some priors hierarchically to allow (for example)
blobs to cluster around a typical central
position, rather than implying a high probability for substructure positions
being spread uniformly (in a frequency sense) over the sky. We also applied
hierarchical priors to the substructure masses (and fluxes) so that, while
the typical order of magnitude of the masses is unknown, the masses
themselves are likely to be roughly the same order of magnitude.
